\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-12-15 Manuscript/Manuscript.tex
added explaination for poisson section

Two types of models were used in \citet{4Buehler2011}, a log-log Ordinary Least Square (OLS) model "with the dependent variable being the bike commuters per 10,000 population. As well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable". This paper analyzed the role of cycling infrastructure on commutership by bike in 90 of the largest 100 U.S. cities. The OLS model is used for estimating coefficients of linear regression that describe the relationship between one or more quantitative independent variables and a dependent variable \cite{XLSTAT2023}. With p explanatory variables, the OLS regression model is: 
\[Y = \beta_{0}+\sum_{j=1,\dots, p}{\beta_{j}X_{j}}+\epsilon\]

@@

\subsection{Zero-inflated Poisson Regression Mode}
\label{sec:pois}

@@

The Poisson model is also used in \citet{9Cantisani2021} to "address the randomness due to the perception and decision of road users at the intersections", as their research is specifically on the crash likelihood of cyclists at roundabouts with different infrastructure types.

>>>>

Two types of models were used in \citet{4Buehler2011}, a log-log Ordinary Least Square (OLS) model "with the dependent variable being the bike commuters per 10,000 population. As well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable". This paper analyzed the role of cycling infrastructure on commuter-ship by bike in 90 of the largest 100 U.S. cities. The OLS model is used for estimating coefficients of linear regression that describe the relationship between one or more quantitative independent variables and a dependent variable \cite{XLSTAT2023}. With p explanatory variables, the OLS regression model is given by equation \ref{eq:1}: 
\begin{equation} \label{eq:1}
Y = \beta_{0}+\sum_{j=1,\dots, p}{\beta_{j}X_{j}}+\epsilon\
\end{equation}

@@

\subsection{Zero-inflated Poisson Regression Model}
\label{sec:pois}

@@

The Poisson model is also used in \citet{9Cantisani2021} to "address the randomness due to the perception and decision of road users at the intersections", as their research is specifically on the crash likelihood of cyclists at roundabouts with different infrastructure types. Zero-inflated models, by assigning a non-zero probability of observing one or more occurrences (like crashes), avoid assuming inherent safety or non-safety in intersections. Due to these reasons, zero-inflated models are useful for analyzing crash count data. It's important to note that zero-inflated models are not as always superior for crash counts, but they are a viable option to consider for bike crash research \cite{Pew_Warr_Schultz_Heaton_2020}.
